---
title: "RExercise#2_Paciente.Rmd"
author: "Francys Chriel Paciente"
date: "2026-09-29"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
##Part A
a<-17
b<-5


a + b
a - b
a * b
a / b
a %% b
a %/% b
2^10
```
Question #1
##17 / 5 results to 3.4, showing decimal quotient. 17 %% 5 results to 2, showing the remainder. 17 %/% 5 results to 3, showing the whole number quotient.

Question #2
##Prediction is correct.

```{r}
##Part B
x<- 42
y <- 42L
z <- "42"
w <- TRUE
v <- 3 + 2i

class(x)
mode(x)
typeof(x)
class(y)
mode(y)
typeof(y)
class(z)
mode(z)
typeof(z)
class(w)
mode(w)
typeof(w)
class(v)
mode(v)
typeof(v)
```
Question #3
## x <- 42 returns as double. y <- 42L returns as integer

Question #4
## typeof() returns low-level storage mode in memory. mode() returns high-level object property. mode() returns functional type category

```{r}
##Part C
num_string <- "123"

num <- as.numeric(num_string)

typeof(num)
class(num)
mode(num)

as.logical(0)
as.logical(1)

bad_string <- "hello123"

as.numeric(bad_string)
```
Question #5
##To prevent the code from crashing and give warning instead.

Question #6
##as.logical(2) results to TRUE, same goes with as.logical(-1).
```{r}
##Part D
fname <- "Juan"
lname <- "Dela Cruz"
age <- 21
ffname <- paste(fname, lname)
cat(fname, lname)

paste(fname, lname)
paste0(fname, lname)

paste(fname, lname, sep = "-")
paste0(ffname, " is ", age, " years old.")
```
Question #7
paste() prints a statement with space or separation. paste0() does not.

Question #8
It made no error. paste() combines values of different data types like character string or numbers. Variable "age" was converted from number to string when resulted to the final text.

```{r}
##Part E version 2
5 + 5
```

Question #9
The error is the first 5 was a string. To fix it, the double quotations must be removed, converting it back to an integer. Now with both 5 + 5, it can correctly show the sum, which is 10.

Question #10
The specified column was read as character data instead of integer or numeric. It should use typeof(), class(), and/or mode() instead to check the type. It will be converted next using as.numeric() and check for any errors before applying it to sum.
